---
title: "Compgenerics study 8 (proportionality) study"
author: Marianna Zhang
date: 2025-03-10
output: 
  html_document:
    toc: true
    toc_float:
      collapsed: false
  word_document:
    toc: true
---

```{r setup, include=FALSE}
# load libraries
library(here)       # navigating directories

library(janitor)    # cleaning data
library(scales)     # percent conversion
library(gt)         # table formatting

library(tidyverse)  # data wrangling & visualization
library(grid)       # custom plotting

library(glmmTMB)    # beta mixed effects models
library(car)        # anova type II-III
library(emmeans)    # pairwise comparisons

# don't show code or messages in knitted doc
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE)

# prevent scientific notation for numerals
options(scipen = 999)

# format p-values for reporting
format_p <- function(p) { 
  if (p < .001) {
    return("< .001")
  } else {
    return(paste0("= ", round(p, digits = 3)))
  }
}
```

```{r vis-theme, include = FALSE}
# set visualization theme
theme_set(
  ggthemes::theme_few() +
    theme(text = element_text(size = 16), # large text size for presentation figures
          axis.ticks.x = element_blank()) # remove x-axis ticks
)
```

# Summary

This exploratory version of study 8 (n=35/condition * 15 conditions = 450 participants) was an exploratory study to assess how count versus proportionality of generics vs specifics affect inductive potential. 

Unlike the previous pilot, we find **an effect of proportion of generics to specifics** on adults' judgments of the prevalence of novel features of a social group. This effect is stronger than the effect of the **raw number of generics** heard, which is a significant predictor on its own, but not after being entered into the same model as proportion (see [Primary results]). 

Notably, proportion continued to be a stronger predictor than raw number of generics, even after subsetting the study to extreme conditions, where proportion (0% or 100%) was a coarser predictor than number of generics (0, or 4/8/16) (see [Extreme conditions only]). 

Nonetheless, the proportionality effect became marginal after controlling for which particular training features were seen (see [Training features]), and was no longer significant after subsetting the study to the mixed conditions, which are more naturalistic and where participants might be particularly sensitive to alternative utterances the speaker could make (see [Mixed conditions only]). 

# Methods

```{r data-import}
# import Qualtrics data
data_raw_headers <- 
  read_csv(here("data", "study8.csv"), 
           n_max = 2) 
  
data_raw <- 
  read_csv(here("data", "study8.csv"),
           col_names = data_raw_headers %>% names(),
           skip = 3) 

# import demographic data from Prolific
data_dem_raw <-
  read_csv(here("data", "study8_dem.csv"))
```

```{r data-cleaning}
data_dem <- data_dem_raw %>% 
  # clean column names
  clean_names() 

data_all <- data_raw %>% 
  
  # join with demographic data
  left_join(data_dem, 
            by = "hashed_id") %>% 
  
  # clean column names
  rename_with(~str_remove(., '_1'),
              .cols = cave_1:attn_check_1) %>% 
  rename(test_features_order = InductionTask_DO) %>% 
  
  # join self-describe demographic columns
  mutate(gender = coalesce(gender_4_TEXT, gender),
         race = coalesce(race_15_TEXT, race)) %>% 
  
  # remove extraneous columns
  select(-c(StartDate:pledge,
            gender_4_TEXT, race_15_TEXT,
            sound_check_DO, check_task_DO, FL_12_DO, # unnecessary display orders
            issues:about,
            submission_id:archived_at,
            completion_code
  )) %>% 
  
  # reorder columns
  relocate(condition:test_features_order,
           .before = cave) %>% 
  
  # add participant ID column
  mutate(participant = row_number(),
         .before = everything()) %>% 
  
  # fix baseline counts
  mutate(num_generics = replace(num_generics, condition=="baseline", 0),
         total_utt = replace(total_utt, condition=="baseline", 0)) %>% 
  
  # convert prevalence to 0-1, trim endpoints
  mutate(across(cave:yellow, \(x) as.numeric(x)/100)) %>% 
  mutate(across(cave:yellow, \(x) case_when(
    x == 0 ~ 0.01,
    x == 1 ~ 0.99,
    TRUE ~ x))) %>%
  
  # fix column types, levels
  mutate(across(c(num_generics, total_utt), as.numeric)) %>% 
  
  mutate(age = age %>% as.numeric(),
         education = education %>% factor(
           levels = c(
             "Less than high school", 
             "High school/GED", 
             "Some college", 
             "Bachelor's (B.A., B.S.)", 
             "Master's (M.A., M.S.)", 
             "Doctoral (Ph.D., J.D., M.D.)", 
             "Prefer not to specify"))) %>% 
  
  # add prop generics, num specifics
  mutate(num_specifics = total_utt - num_generics,
         .before = total_utt) %>% 
  mutate(prop_generics = num_generics/total_utt,
         .after = total_utt) 


# # unpack order into lists
# mutate(across(ends_with("order")),
#        str_split_1(., '\\|'))
```


## Participants

```{r sample}
# record total collected, failures on each check question
sample <- data_all %>% 
  summarize(n_collect = n(),
            # sound_check = sum(sound_check != "bird" | is.na(sound_check)),
            attn_check = sum(attn_check != 100 | is.na(attn_check)),
            AI = sum(AI != "No" | is.na(AI)),
            check_task = sum(check_task != "Answering questions about a fictional group of people"))

# exclude participants
data <- data_all %>%
  filter(
    # sound_check == "bird",
    attn_check == 100,
    AI == "No",
    check_task == "Answering questions about a fictional group of people") %>% 
  select(-c(sound_check, attn_check, AI, check_task))

# record number of participants in actual sample after exclusions, exclusion rate
sample <- sample %>% 
  mutate(n = nrow(data),
         n_excl = n_collect - n,
         excl_rate = n_excl/n_collect)
```

Data was collected from `r sample$n_collect` adults (n=8-11/condition) via Prolific on Monday 3/10/2025. Participants required to be in the United States, fluent in English, and having not participated in prior studies under this protocol. Participants were paid $1.63 for an estimated 5-8 minute task. Participants were requested to particpate via desktop, after reported iOS issues on the last task. 

```{r sample-condition}
# Record number of participants in actual sample per condition
sample_condition <- data %>% 
  group_by(num_generics, total_utt) %>% 
  summarize(n = length(unique(participant)))

sample_condition %>% 
  ungroup() %>% 
  gt()
```

### Exclusion criteria

We recruited 525 participants, of whom `r sample$n_excl` participants (`r label_percent(0.1) (sample$excl_rate)` of all participants) were excluded for meeting at least 1 of the following exclusion criteria:

* failing the attention check (i.e., did not select 100% on slider when asked to during induction task) (n = `r sample$attn_check` participants)

* admitting to use of AI after being explicitly informed use was prohibited (n = `r sample$AI` participants)

* failing the task check (n = `r sample$check_task` participants)

Participants who failed the sound check were included, since a few participants mentioned technical difficulties with the Qualtrics automatically progressing past that video. 

### Demographics

```{r dem-age}
## Age
dem_age <- data %>%
  summarize(mean = mean(age),
            sd = sd(age),
            n = n())

data %>% 
  ggplot(aes(x = age)) +
  geom_density() +
  scale_x_continuous(limits = c(18, 100))

dem_age %>%
  gt() %>% 
  tab_header("age") %>% 
  fmt_number(
    columns = mean:sd,
    decimals = 2,
    use_seps = FALSE
  )
```
* The sample skewed young in age. 

```{r dem-gender}
## Gender
dem_gender <- data %>%
  count(gender, sort = TRUE) %>% 
  mutate(prop = n/sample$n)

dem_gender %>% 
  mutate(prop = label_percent(0.1) (prop)) %>% 
  gt() 
```

* The sample reflected the diversity of the gender identities in the US.

[(`r label_percent() (dem_gender %>% filter(gender == "Male") %>% pull(prop))` male, `r label_percent() (dem_gender %>% filter(gender == "Female") %>% pull(prop))` female, `r label_percent() (dem_gender %>% filter(gender == "Non-binary") %>% pull(prop))` non-binary, `r label_percent() (dem_gender %>% filter(gender == "Prefer not to specify") %>% pull(prop))` prefer not to specify)]: # 

```{r dem-race}
## Race
dem_race <- data %>%
  count(race, sort = TRUE) %>% 
  mutate(prop = n/sample$n)

dem_race_lumped <- data %>%
  mutate(race_lumped = fct_lump_prop(race, 0.025)) %>%
  count(race_lumped, sort = TRUE) %>% 
  mutate(prop = n/sample$n)

dem_race %>% 
  mutate(prop = label_percent(0.1) (prop)) %>% 
  gt() 
```

* The sample was also racially diverse, with White Americans slightly overrepresented and Hispanic Americans undererepresented. 

[`r label_percent() (dem_race %>% filter(race == "White, Caucasian, or European American") %>% pull(prop))` White, Caucasian or European American; `r label_percent() (dem_race %>% filter(race == "Black or African American") %>% pull(prop))` Black or African American, `r label_percent() (dem_race %>% filter(race == "Hispanic or Latino/a") %>% pull(prop))` Hispanic or Latino/a, `r label_percent() (dem_race %>% filter(race == "East Asian") %>% pull(prop))` East Asian, `r label_percent() (dem_race %>% filter(race == "South or Southeast Asian") %>% pull(prop))` South or Southeast Asian.]: #

```{r dem-education}
## Education
dem_education <- data %>%
  count(education) %>% 
  mutate(prop = n/sample$n)

dem_education %>% 
  mutate(prop = label_percent(0.1) (prop)) %>% 
  gt() 
```

* The sample was about evenly split on college completion. 

## Procedure

This study was administered as a [Qualtrics survey](https://nyu.qualtrics.com/survey-builder/SV_eCL8bIiwGScAj7o/edit), and approved by the NYU IRB (IRB-FY2023-6812).

After providing their consent, participants completed a captcha, pledge not to use AI, and sound check. Participants then completed:

1. **Training phase**: participants heard some number of generic statements and specific statements, based on condition. Which features were mentioned was randomized, as was statement order.

2. **Test phase (induction task)**: participants completed an induction task where they imagined seeing a Zarpie with a novel feature, and estimated the prevalence of that feature among Zarpies using a slider from 0 to 100 (initialized at 0). All participants completed the same 16 trials, with order of trials randomized. 

Participants then completed a few task completion questions, demographics, and were debriefed. 

## Data processing

Prevalence judgments were converted to a scale from 0 to 1, with 0 and 1 values trimmed to 0.01 and 0.99 to support a beta regression, since a uniform beta distribution does not include its endpoints of 0 and 1. 

## Participant feedback

The most frequent participant issue was audio issues (*n* = 4). One participant reported "The audio was horrible. It scared my cat.", another reported "you might want to equalize the volume between the videos and the questions" (I had noticed equalization issues but was unable to fix in HTML, will fix later in the video itself). 

One person had trouble with the attention check ("I couldn't see where to move the slider for the attention check, so I just chose 50%"). 

One person complained that they were unable to copy the consent form (this issue was a result of anti-AI study-wide CSS and will be changed to question-specific CSS in the future). 

When asked to guess what the study was about, many participants reported that it was about judging other people by their characteristics. 

# Primary results

## Induction task

### Plots {.tabset}

```{r data-tidy}
data_tidy <- data %>% 
  # tidy data
  pivot_longer(cols = cave:yellow,
               names_to = "test_feature",
               values_to = "prevalence") %>% 
  # extract the order of test features (disregarding attention check)
  mutate(test_feature_order = map2_int(test_feature, test_features_order,
                                       function(feat, order){
                                         order_split <- str_split_1(order, '\\|') %>% # split test_features_order by |
                                           discard(\(x) x == "attn_check") # discard attention check
                                         match(feat, order_split)[1] # get first matching index
                                       })) %>% 
  select(-test_features_order)

data_tidy %>% 
  write_csv(here("data/processed", "study8_tidy.csv"))
```


#### Summary

```{r plot-induction-num}
# summary plot of prevalence by condition (number of generics)
data_tidy %>% 
  
  # convert num_generics to factor
  mutate(num_generics = as.factor(num_generics)) %>%
  
  # make plot
  ggplot(aes(y = prevalence,
             x = total_utt,
             color = num_generics)) + 
  
  # add confidence intervals + means
  stat_summary(fun = mean,
               geom = "line",
               aes(group = num_generics),
               position = position_dodge(width = 1),
               size = 1) +
  stat_summary(fun.data = mean_cl_boot,
               geom = "linerange",
               position = position_dodge(width = 1),
               size = 1) +
  stat_summary(fun = mean,
               geom = "point",
               position = position_dodge(width = 1),
               size = 2) +
  
  # color palette
  scale_color_viridis_d(name = "number \nof generics",
                        end = .8,
                        option = "magma") +
  
  # customize axes
  theme(legend.title = element_text(size = 14),
        legend.text = element_text(size = 12),
        plot.caption = element_text(size = 8)) +
  scale_x_continuous(name = "total utterances",
                     breaks = c(0, 4, 8, 12, 16)) + # conditions
  scale_y_continuous(name = "prevalence",
                     limits = c(0, 1),
                     breaks = c(0, .25, .5, .75, 1), # labelled points on slider
                     labels = percent) +
  
  # add title
  ggtitle("Prevalence by number of generics") +
  labs(caption = "baseline, 0/16, 16/16 = replication of Study 6
       collapsing across 16 test features")

ggsave(path = "figs",
       filename = "prevalence_by_number.png")
```

```{r plot-induction-prop}
# summary plot of prevalence by condition (prop generics)
data_tidy %>% 
  
  mutate(prop_generics = case_when(is.na(prop_generics) ~ "baseline",
                                   TRUE ~ as.character(round(prop_generics, 2))) %>% 
           as.factor()) %>% 
  
  # make plot
  ggplot(aes(y = prevalence,
             x = total_utt,
             color = prop_generics)) + 
  
  # add confidence intervals + means + lines connecting means
  
  stat_summary(fun = mean,
               geom = "line",
               aes(group = prop_generics),
               position = position_dodge(width = 1),
               size = 1) +
  stat_summary(fun.data = mean_cl_boot,
               geom = "linerange",
               position = position_dodge(width = 1),
               size = 1) +
  stat_summary(fun = mean,
               geom = "point",
               position = position_dodge(width = 1),
               size = 2) +
  
  # color palette
  scale_color_viridis_d(name = "proportion\nof generics,\nvs specifics",
                        end = .8,
                        option = "magma") +
  
  # customize axes
  theme(legend.title = element_text(size = 14),
        legend.text = element_text(size = 12),
        plot.caption = element_text(size = 8)) +
  scale_x_continuous(name = "total utterances",
                     breaks = c(0, 4, 8, 12, 16)) + # conditions
  scale_y_continuous(name = "prevalence",
                     limits = c(0, 1),
                     breaks = c(0, .25, .5, .75, 1), # labelled points on slider
                     labels = percent) +
  
  # add title
  ggtitle("Prevalence by proportion of generics") +
  labs(caption = "baseline, 0/16, 16/16 = replication of Study 6
       collapsing across 16 test features")

ggsave(path = "figs",
       filename = "prevalence_by_prop.png")
```

#### Density

```{r plot-induction-density}
# density plot of prevalence by condition
data_tidy %>% 
  # reverse num_generics for plotting
  mutate(num_generics = factor(num_generics,
                               levels=sort(unique(data_tidy$num_generics),
                                           decreasing = TRUE))) %>% 
  # add condition highlight for Study 6 conditions
  mutate(condition_highlight = case_when(condition %in% c("baseline", "0/16", "16/16") ~ "yes",
                                         TRUE ~ "no")) %>% 
  
  # make plot
  ggplot(aes(x = prevalence,
             fill = prop_generics)) + 
  facet_grid(num_generics ~ total_utt) +
  
  # add background highlight to specific facets
  geom_rect(aes(xmin = -Inf, xmax = Inf,
                ymin = -Inf, ymax = Inf,
                alpha = condition_highlight),
            fill = "lightyellow") +
  scale_alpha_manual(values = c(0, 0.1)) +
  
  # add facet outline to specific facets (writes under facet outlines)
  # geom_rect(aes(xmin = -Inf, xmax = Inf,
  #               ymin = -Inf, ymax = Inf,
  #               alpha = condition_highlight),
  #           color = "yellow",
  #           fill = NA,
  #           inherit.aes = FALSE) + 
  # scale_alpha_manual(values = c(0, 1)) + 
  
  # add density plots
  geom_density(adjust = 1/2) + 
  scale_fill_gradient(name = "proportion\n of generics,\n vs specifics\n",
                      low = "#1f77b4", high = "#ff7f0e") +
  
  # remove default facet row/column strip labels...
  theme(
    strip.background = element_blank(),
    strip.text.x = element_blank(),
    strip.text.y = element_blank(),
  ) +
  # ...in favor of in-facet labels
  geom_text(data = data_tidy %>% distinct(condition, prop_generics, 
                                          num_generics, total_utt),
            aes(label = if_else(
              condition == "baseline", "baseline",
              glue::glue('{condition} generics'))),
            x = .5, y = Inf, vjust = 1.5, size = 3) +
  # annotate('text', x = 50, y = Inf,  vjust = 1.5, size = 3,
  #          label = unique(data_tidy$condition)) +
  
  # customize axes
  theme(legend.title = element_text(size = 14),
        legend.text = element_text(size = 12),
        axis.title.x = element_text(size = 10),
        axis.minor.ticks.x.bottom = element_line(size = .5), 
        axis.text.x = element_text(size = 8, hjust = c(0, 1), vjust = .8),
        plot.caption = element_text(size = 8)) +
  scale_y_continuous(name = "number of generics",
                     breaks = NULL,
                     expand = c(0, 0, 0.3, 0)) +
  scale_x_continuous(breaks = c(0, 1), 
                     minor_breaks = c(.25, .5, .75), # labelled points on slider
                     expand = c(0,0),
                     labels = percent) +
  guides(
    x = guide_axis(minor.ticks = TRUE),
    alpha = "none"
  ) +
  
  # add title
  ggtitle("Prevalence by condition") +
  labs(caption = "baseline, 0/16, 16/16 = replication of Study 6
       collapsing across 16 test features")

ggsave(path = "figs",
       filename = "prevalence_density_by_condition.png")

# add facet outline to specific facets (does not work)
# g <- ggplotGrob(p)
# str(g$grobs[[6]])
# g$grobs[[6]]$children[[1]]$children[[1]]$gp$col <- "yellow"
# grid.draw(g)
```

#### Histogram

```{r plot-induction-hist}
# histogram of prevalence by condition
data_tidy %>% 
  # reverse num_generics for plotting
  mutate(num_generics = factor(num_generics,
                               levels=sort(unique(data_tidy$num_generics),
                                           decreasing = TRUE))) %>% 
  # add condition highlight for Study 6 conditions
  mutate(condition_highlight = case_when(condition %in% c("baseline", "0/16", "16/16") ~ "yes",
                                         TRUE ~ "no")) %>% 
  
  # make plot
  ggplot(aes(x = prevalence,
             fill = prop_generics)) + 
  facet_grid(num_generics ~ total_utt) +
  
  # add background highlight to specific facets
  geom_rect(aes(xmin = -Inf, xmax = Inf,
                ymin = -Inf, ymax = Inf,
                alpha = condition_highlight),
            fill = "lightyellow") +
  scale_alpha_manual(values = c(0, 0.1)) +
  
  # add hist
  geom_histogram(binwidth = .1) + 
  scale_fill_gradient(name = "proportion\n of generics,\n vs specifics\n",
                      low = "#1f77b4", high = "#ff7f0e") +
  
  # remove default facet row/column strip labels...
  theme(
    strip.background = element_blank(),
    strip.text.x = element_blank(),
    strip.text.y = element_blank(),
  ) +
  # ...in favor of in-facet labels
  geom_text(data = data_tidy %>% distinct(condition, prop_generics, 
                                          num_generics, total_utt),
            aes(label = if_else(
              condition == "baseline", "baseline",
              glue::glue('{condition} generics'))),
            x = .5, y = Inf, vjust = 1.5, size = 3) +
  # annotate('text', x = 50, y = Inf,  vjust = 1.5, size = 3,
  #          label = unique(data_tidy$condition)) +
  
  # customize axes
  theme(legend.title = element_text(size = 14),
        legend.text = element_text(size = 12),
        axis.title.x = element_text(size = 10),
        axis.minor.ticks.x.bottom = element_line(size = .5), 
        axis.text.x = element_text(size = 8, hjust = c(0, 1), vjust = .8),
        plot.caption = element_text(size = 8)) +
  scale_y_continuous(name = "number of generics",
                     breaks = NULL,
                     expand = c(0, 0, 0.3, 0)) +
  scale_x_continuous(breaks = c(0, 1), 
                     minor_breaks = c(.25, .5, .75), # labelled points on slider
                     expand = c(0,0),
                     labels = percent) +
  guides(
    x = guide_axis(minor.ticks = TRUE),
    alpha = "none"
  ) +
  
  # add title
  ggtitle("Prevalence by condition") +
  labs(caption = "baseline, 0/16, 16/16 = replication of Study 6
       collapsing across 16 test features")

ggsave(path = "figs",
       filename = "prevalence_hist_by_condition.png")
```

#### Cumulative
```{r plot-induction-cum}
# cumulative prevalence by condition
data_tidy %>% 
  # reverse num_generics for plotting
  mutate(num_generics = factor(num_generics,
                               levels=sort(unique(data_tidy$num_generics),
                                           decreasing = TRUE))) %>% 
  # add condition highlight for Study 6 conditions
  mutate(condition_highlight = case_when(condition %in% c("baseline", "0/16", "16/16") ~ "yes",
                                         TRUE ~ "no")) %>% 
  
  # add cumulative counts
  arrange(num_generics, total_utt, prevalence) %>% 
  group_by(num_generics, total_utt) %>% 
  mutate(prevalence_cum_pct = row_number()/n()) %>% 
  # mutate(cum_prevalence = cumsum(prevalence)) %>% 
  ungroup() %>% 
  
  # make plot
  ggplot(aes(x = prevalence,
             y = prevalence_cum_pct,
             color = prop_generics)) + 
  facet_grid(num_generics ~ total_utt) +
  
  # add background highlight to specific facets
  geom_rect(aes(xmin = -Inf, xmax = Inf,
                ymin = -Inf, ymax = Inf,
                alpha = condition_highlight),
            fill = "lightyellow") +
  scale_alpha_manual(values = c(0, 0.1)) +
  
  # draw cumulative distribution
  geom_line() + 
  
  scale_color_gradient(name = "proportion\n of generics,\n vs specifics\n",
                       low = "#1f77b4", high = "#ff7f0e") +
  
  # remove default facet row/column strip labels...
  theme(
    strip.background = element_blank(),
    strip.text.x = element_blank(),
    strip.text.y = element_blank(),
  ) +
  # ...in favor of in-facet labels
  geom_text(data = data_tidy %>% distinct(condition, prop_generics, 
                                          num_generics, total_utt),
            aes(label = if_else(
              condition == "baseline", "baseline",
              glue::glue('{condition} generics'))),
            x = .5, y = Inf, vjust = 1.5, size = 3) +
  
  # customize axes
  theme(legend.title = element_text(size = 14),
        legend.text = element_text(size = 12),
        axis.title.x = element_text(size = 10),
        axis.minor.ticks.x.bottom = element_line(size = .5), 
        axis.text.x = element_text(size = 8, hjust = c(0, 1), vjust = .8),
        plot.caption = element_text(size = 8)) +
  scale_y_continuous(name = "number of generics",
                     breaks = NULL,
                     expand = c(0, 0, 0.3, 0)) +
  scale_x_continuous(breaks = c(0, 1), minor_breaks = c(.25, .5, .75), expand = c(0,0),
                     labels = label_percent()) +
  guides(
    x = guide_axis(minor.ticks = TRUE),
    alpha = "none"
  ) +
  
  # add title
  ggtitle("Prevalence by condition") +
  labs(caption = "baseline, 0/16, 16/16 = replication of Study 6
       collapsing across 16 test features")

ggsave(path = "figs",
       filename = "prevalence_cum_by_condition.png")
```

```{r plot-induction-cum-prop}
# plot prevalence (cumulative) by prop generics
data_tidy %>% 
  # reverse num_generics for plotting
  mutate(num_generics = factor(num_generics,
                               levels=sort(unique(data_tidy$num_generics),
                                           decreasing = TRUE))) %>% 
  
  # add cumulative counts
  arrange(num_generics, total_utt, prevalence) %>% 
  group_by(num_generics, total_utt) %>% 
  mutate(prevalence_cum_pct = row_number()/n()) %>% 
  # mutate(cum_prevalence = cumsum(prevalence)) %>% 
  ungroup() %>% 
  
  # make plot
  ggplot(aes(x = prevalence,
             y = prevalence_cum_pct,
             color = num_generics)) + 
  facet_wrap(vars(prop_generics), 
             nrow = n_distinct(data_tidy$prop_generics)) +
  
  # draw cumulative distribution
  geom_line(aes(group = condition)) + 
  
  # scale_color_gradient(name = "proportion\n of generics,\n vs specifics\n",
  #                      low = "#1f77b4", high = "#ff7f0e") +
  
  # remove default facet row/column strip labels...
  theme(
    strip.background = element_blank(),
    strip.text.x = element_blank(),
    strip.text.y = element_blank(),
  ) +
  # ...in favor of in-facet labels
  geom_text(data = data_tidy %>% 
              distinct(condition, prop_generics, num_generics, total_utt) %>% 
              group_by(prop_generics) %>% 
              summarize(facet_label = paste(condition, collapse = ', ')),
            aes(label = facet_label),
            x = .5, y = Inf, vjust = 1.5, size = 3, inherit.aes = F) +
  
  # customize axes
  theme(legend.title = element_text(size = 14),
        legend.text = element_text(size = 12),
        axis.title.x = element_text(size = 10),
        axis.minor.ticks.x.bottom = element_line(size = .5), 
        axis.text.x = element_text(size = 8, hjust = c(0, 1), vjust = .8),
        plot.caption = element_text(size = 8)) +
  scale_y_continuous(name = "proportion of generics to specifics",
                     breaks = NULL,
                     expand = c(0, 0, 0.3, 0)) +
  scale_x_continuous(breaks = c(0, 1), minor_breaks = c(.25, .5, .75), expand = c(0,0),
                     labels = label_percent()) +
  guides(
    x = guide_axis(minor.ticks = TRUE),
    alpha = "none"
  ) +
  
  # add title
  ggtitle("Prevalence by proportion of generics to specifics") +
  labs(caption = "baseline, 0/16, 16/16 = replication of Study 6
       collapsing across 16 test features")

ggsave(path = "figs",
       filename = "prevalence_cum_by_prop.png",
       height = 7,
       width = 3)
```

```{r plot-induction-cum-count}
# plot prevalence (cumulative) by number of generics
data_tidy %>% 
  # reverse num_generics for plotting
  mutate(num_generics = factor(num_generics,
                               levels=sort(unique(data_tidy$num_generics),
                                           decreasing = TRUE))) %>% 
  
  # add cumulative counts
  arrange(num_generics, total_utt, prevalence) %>% 
  group_by(num_generics, total_utt) %>% 
  mutate(prevalence_cum_pct = row_number()/n()) %>% 
  # mutate(cum_prevalence = cumsum(prevalence)) %>% 
  ungroup() %>% 
  
  # make plot
  ggplot(aes(x = prevalence,
             y = prevalence_cum_pct,
             color = prop_generics)) + 
  facet_wrap(vars(num_generics), 
             nrow = n_distinct(data_tidy$num_generics)) +
  
  # draw cumulative distribution
  geom_line(aes(group = condition)) + 
  
  scale_color_gradient(name = "proportion\n of generics,\n vs specifics\n",
                       low = "#1f77b4", high = "#ff7f0e") +
  
  # remove default facet row/column strip labels...
  theme(
    strip.background = element_blank(),
    strip.text.x = element_blank(),
    strip.text.y = element_blank(),
  ) +
  # ...in favor of in-facet labels
  geom_text(data = data_tidy %>% 
              distinct(condition, prop_generics, num_generics, total_utt) %>% 
              group_by(num_generics) %>% 
              summarize(facet_label = paste(condition, collapse = ', ')),
            aes(label = facet_label),
            x = .5, y = Inf, vjust = 1.5, size = 3, inherit.aes = F) +
  
  # customize axes
  theme(legend.title = element_text(size = 14),
        legend.text = element_text(size = 12),
        axis.title.x = element_text(size = 10),
        axis.minor.ticks.x.bottom = element_line(size = .5), 
        axis.text.x = element_text(size = 8, hjust = c(0, 1), vjust = .8),
        plot.caption = element_text(size = 8)) +
  scale_y_continuous(name = "number of generics",
                     breaks = NULL,
                     expand = c(0, 0, 0.3, 0)) +
  scale_x_continuous(breaks = c(0, 1), minor_breaks = c(.25, .5, .75), expand = c(0,0),
                     labels = percent) +
  guides(
    x = guide_axis(minor.ticks = TRUE),
    alpha = "none"
  ) +
  
  # add title
  ggtitle("Prevalence by number of generics") +
  labs(caption = "baseline, 0/16, 16/16 = replication of Study 6
       collapsing across 16 test features")

ggsave(path = "figs",
       filename = "prevalence_cum_by_count.png",
       height = 10,
       width = 3.5)
```


### Analyses

The following beta regressions predict prevalence with random intercepts per participant and per test feature. 

* There is a main effect of **condition** ($\chi$(14)=43.69, *p*<.001) on the inferred prevalence of novel features. 

* On their own as lone predictors, **raw number of generics** (*z* = 5.34, *p* < .001), the **raw number of specifics** (*z* = -4.25, *p* < .001), and the **proportion of generics to specifics** (*z* = 5.68, *p* < .001) each predicted the inferred prevalence of novel features.

* When entered into the same model, **proportion of generics to specifics** predicted prevalence judgments (*z* = 2.36, *p* = .018), while **raw number of generics** did not (*z* = 0.99, *p* = .32). (This is the reverse of the pattern from the pilot.)

* When entered into the same model, **raw number of generics** predicted prevalence judgments (*z* = 3.69, *p* < .001), while raw number of specifics was marginal (*z* = -1.86, *p* = .063).

```{r analysis-initial, echo = TRUE, include = TRUE}
# condition
glmmTMB(prevalence ~ condition + (1|participant) + (1|test_feature), 
        data = data_tidy, 
        family = beta_family(link = "logit")) %>% 
  Anova()
```

```{r analysis-simple, echo = TRUE, include = TRUE}
# raw number of generics
glmmTMB(prevalence ~ num_generics + (1|participant) + (1|test_feature),
        data = data_tidy, 
        family = beta_family(link = "logit")) %>% 
  summary()

# raw number of specifics
glmmTMB(prevalence ~ num_specifics + (1|participant) + (1|test_feature),
        data = data_tidy, 
        family = beta_family(link = "logit")) %>% 
  summary()

# proportion of generics
glmmTMB(prevalence ~ prop_generics + (1|participant) + (1|test_feature),
        data = data_tidy, 
        family = beta_family(link = "logit")) %>% 
  summary()
```

```{r analysis-num-vs-prop-generics, echo = TRUE, include = TRUE}
# raw number vs proportion of generics
glmmTMB(prevalence ~ num_generics + prop_generics + (1|participant) + (1|test_feature),
        data = data_tidy, 
        family = beta_family(link = "logit")) %>% 
  summary()
```


```{r analysis-generics-vs-specifics, echo = TRUE, include = TRUE}
# raw number of generics vs raw number of specifics
glmmTMB(prevalence ~ num_generics + num_specifics + (1|participant) + (1|test_feature),
        data = data_tidy, 
        family = beta_family(link = "logit")) %>% 
  summary()
```


# Secondary results


## Straight-lining

```{r straightlining}
# exact straightlining (50)
straightline_50_participants <-
  data_tidy %>% 
  group_by(participant) %>%
  filter(all(prevalence == 0.50)) %>% 
  distinct(participant)

# approximate straightlining (48-52)
straightline_approx_participants <-
  data_tidy %>% 
  group_by(participant) %>%
  filter(all(prevalence %in% seq(0.48, 0.52, 0.01))) %>% 
  distinct(participant)
```

Induction task plots suggest a lot of anchoring around the 50\% marker, and debriefing suggests many participants thought it was a strange task since the test features were odd/bizarre. Are these just from participants who were straightlining through all the test items? 

* `r straightline_50_participants %>% nrow()` out of `r sample$n` included participants (`r label_percent(0.01)(nrow(straightline_50_participants)/sample$n)`) answered 50\% to all test questions. 

* `r straightline_approx_participants %>% nrow()` out of `r sample$n` included participants (`r label_percent(0.01)(nrow(straightline_approx_participants)/sample$n)`) answered 48-52% to all test questions, a looser criterion.

Since there were only a few participants who consistently straightlined, these participants were not excluded from analyses. 


## Pairwise condition comparisons

```{r ks-test-num}
# get all conditions
condition_names <- data_tidy %>% 
  arrange(num_generics, total_utt) %>%
  pull(condition) %>% 
  unique()

# construct all pairs of conditions
condition_pairs <- 
  combn(condition_names, 2) %>% 
  t() %>% # transpose
  as.tibble() %>% 
  rename(condition_1 = `V1`,
         condition_2 = `V2`)

# define function to run ks test and return test results
get_ks_results <- function(condition_a, condition_b){
  # run ks test on cumulative percents from each condition
  ks_test <- ks.test(data_tidy %>%
                       filter(condition == condition_a) %>%
                       pull(prevalence),
                     data_tidy %>%
                       filter(condition == condition_b) %>%
                       pull(prevalence))
  
  # store results
  ks_results <- tibble(
    condition_1 = condition_a,
    condition_2 = condition_b,
    D = ks_test$statistic,
    p.value = ks_test$p.value,
    p.value.exact = ks_test$exact
  )
  
  return(ks_results)
}

# run the function using the condition pairs
condition_pairs_results <- tibble(
  ks_results = map2(condition_pairs$condition_1, condition_pairs$condition_2, 
                    get_ks_results)) %>%
  unnest(cols = c(ks_results)) %>% 
  
  # add p-value sig column
  mutate(p.value_sig = (p.value < .05),
         p.value_corr = (p.value * nrow(.)),
         p.value_sig_corr = (p.value_corr < .05)) %>% 
  
  # join additional condition columns for condition_1
  left_join(
    data_tidy %>% 
      distinct(condition, num_generics, prop_generics) %>%
      rename(
        condition_1 = condition,
        condition_1_num_generics = num_generics,
        condition_1_prop_generics = prop_generics,
      ),
    by = "condition_1"
  ) %>%
  
  # join additional condition columns for condition_1
  left_join(
    data_tidy %>% 
      distinct(condition, num_generics, prop_generics) %>%
      rename(
        condition_2 = condition,
        condition_2_num_generics = num_generics,
        condition_2_prop_generics = prop_generics
      ),
    by = "condition_2"
  ) %>% 
  
  # add match columns
  mutate(same_num_generics = (condition_1_num_generics == condition_2_num_generics),
         same_prop_generics = (condition_1_prop_generics == condition_2_prop_generics)) %>%
  
  # reorder columns
  relocate(starts_with("condition_1"), starts_with("condition_2"), starts_with("same"), everything())
```

```{r ks-test-prop}
# get all conditions
condition_names_prop <- data_tidy %>% 
  arrange(prop_generics, num_generics, total_utt) %>%
  pull(condition) %>% 
  unique()

condition_names_prop <- c(
  condition_names_prop[length(condition_names_prop)],
  condition_names_prop[-length(condition_names_prop)]) # move baseline first


# construct all pairs of conditions
condition_pairs_prop <- 
  combn(condition_names_prop, 2) %>% 
  t() %>% # transpose
  as.tibble() %>% 
  rename(condition_1 = `V1`,
         condition_2 = `V2`)

# define function to run ks test and return test results
get_ks_results <- function(condition_a, condition_b){
  # run ks test on cumulative percents from each condition
  ks_test <- ks.test(data_tidy %>%
                       filter(condition == condition_a) %>%
                       pull(prevalence),
                     data_tidy %>%
                       filter(condition == condition_b) %>%
                       pull(prevalence))
  
  # store results
  ks_results <- tibble(
    condition_1 = condition_a,
    condition_2 = condition_b,
    D = ks_test$statistic,
    p.value = ks_test$p.value,
    p.value.exact = ks_test$exact
  )
  
  return(ks_results)
}

# run the function using the condition pairs
condition_pairs_prop_results <- tibble(
  ks_results = map2(condition_pairs_prop$condition_1, condition_pairs_prop$condition_2, 
                    get_ks_results)) %>%
  unnest(cols = c(ks_results)) %>% 
  
  # add p-value sig column
  mutate(p.value_sig = (p.value < .05),
         p.value_corr = (p.value * nrow(.)),
         p.value_sig_corr = (p.value_corr < .05)) %>% 
  
  # join additional condition columns for condition_1
  left_join(
    data_tidy %>% 
      distinct(condition, num_generics, prop_generics) %>%
      rename(
        condition_1 = condition,
        condition_1_num_generics = num_generics,
        condition_1_prop_generics = prop_generics,
      ),
    by = "condition_1"
  ) %>%
  
  # join additional condition columns for condition_1
  left_join(
    data_tidy %>% 
      distinct(condition, num_generics, prop_generics) %>%
      rename(
        condition_2 = condition,
        condition_2_num_generics = num_generics,
        condition_2_prop_generics = prop_generics
      ),
    by = "condition_2"
  ) %>% 
  
  # add match columns
  mutate(same_num_generics = (condition_1_num_generics == condition_2_num_generics),
         same_prop_generics = (condition_1_prop_generics == condition_2_prop_generics)) %>%
  
  # reorder columns
  relocate(starts_with("condition_1"), starts_with("condition_2"), starts_with("same"), everything())
```

We can make **pairwise comparisons between conditions** using two-sample Kolmogorov–Smirnov tests, with Bonferroni correction for number of tests run (`r nrow(condition_pairs_results)`). The Kolmogorov–Smirnov test compares the cumulative distributions of two samples and returns a statistic *D* that reflects the maximum difference between the two distributions, as well as a *p*-value for the test.

```{r ks-test-plot-num}
# group same number of generics
group_boundaries <- data.frame(
  xmin = c(0.5, 4.5, 8.5, 11.5),  # start of each group
  xmax = c(4.5, 8.5, 11.5, 13.5), # end of each group
  ymin = c(0.5, 5.5, 9.5, 12.5),  # start of each group
  ymax = c(5.5, 9.5, 12.5, 14.5)  # end of each group
)

# plotting confusion matrix-style plot for K-S test
condition_pairs_results %>% 
  mutate(across(c(condition_1, condition_2), 
                ~ factor(.x, levels = condition_names))) %>%
  ggplot(aes(x = condition_2, y = condition_1, 
             fill = D)) +
  geom_tile(linewidth = 1.01) +
  # add border for groups of tiles w same num_generic
  geom_rect(data = group_boundaries,
            aes(xmin = xmin, xmax = xmax,
                ymin = ymin, ymax = ymax),
            fill = NA,
            color = "black",
            linewidth = 1,
            inherit.aes = FALSE) +
  
  # label D and p-value
  scale_fill_viridis_c(name = "D",
                       limits = c(0, .32)) +
  geom_text(aes(label = case_when(p.value_corr < .001 ~ "***",
                                  p.value_corr < .01 ~ "**",
                                  p.value_corr < .05 ~ "*",
                                  TRUE ~ ""))) + 
  # custom axes
  scale_x_discrete(name = "condition") + 
  scale_y_discrete(name = "condition") +
  ggtitle("Pairwise comparisons between conditions",
          "ordered by number of generics") +
  labs(caption = "Kolmogorov–Smirnov tests w/ Bonferroni correction\nD = maximum percentage distance between cumulative curves \n* = p-value") 

ggsave("condition_pairs_num.png")
```

```{r ks-test-plot-prop}
# group same prop generics
group_boundaries <- data.frame(
  xmin = c(0.5, 6.5, 10.5),  # start of each group
  xmax = c(4.5, 8.5, 14.5), # end of each group
  ymin = c(1.5, 7.5, 11.5),  # start of each group
  ymax = c(5.5, 9.5, 14.5)  # end of each group
)

# plotting confusion matrix-style plot for K-S test
condition_pairs_prop_results %>% 
  mutate(across(c(condition_1, condition_2), 
                ~ factor(.x, levels = condition_names_prop))) %>%
  ggplot(aes(x = condition_2, y = condition_1, 
             fill = D)) +
  geom_tile(linewidth = 1.01) +
  # add border for groups of tiles w same num_generic
  geom_rect(data = group_boundaries,
            aes(xmin = xmin, xmax = xmax,
                ymin = ymin, ymax = ymax),
            fill = NA,
            color = "black",
            linewidth = 1,
            inherit.aes = FALSE) +
  
  # label D and p-value
  scale_fill_viridis_c(name = "D",
                       limits = c(0, .32)) +
  geom_text(aes(label = case_when(p.value_corr < .001 ~ "***",
                                  p.value_corr < .01 ~ "**",
                                  p.value_corr < .05 ~ "*",
                                  TRUE ~ ""))) + 
  # custom axes
  scale_x_discrete(name = "condition") + 
  scale_y_discrete(name = "condition") +
  ggtitle("Pairwise comparisons between conditions",
          "ordered by proportion of generics to specifics") +
  labs(caption = "Kolmogorov–Smirnov tests w/ Bonferroni correction\nD = maximum percentage distance between cumulative curves \n* = p-value") 

ggsave("condition_pairs_prop.png")
```

One quick and dirty way to think about these results is to look at how often pairs of conditions with the *same* (boxed) versus *different* (not in box) number of generics are significantly different from each other, and to do the same for pairs of conditions with *same* (boxed) versus *different* (not in box) proportions of generics. 

Note, there are way way more pairwise comparisons comparing *different* numbers or proportions of generics than *same* numbers or proportion of generics, so this is a bit of a lopsided comparison. 

If say number of generics matters, we would expect to see that the distribution of prevalence ratings rarely differ when comparing pairs that are the *same* number of generics, and differ much more when comparing pairs that are *different* number of generics.

If say proportion of generics matters, we would expect to see that the distribution of prevalence ratings rarely differ when comparing pairs that are the *same* proportion of generics, and differ much more when comparing pairs that are *different* proportion of generics.

```{r ks-test-summary}
# how often is the test significantly different (after correction) pairs with same vs diff number of generics
condition_pairs_results %>% 
  group_by(same_num_generics) %>% 
  summarize(sig_corr_tests = sum(p.value_sig_corr),
            total_tests = n(),
            prop_sig_corr = sig_corr_tests/total_tests) %>% 
  
  # pretty table
  gt() %>% 
  fmt_percent(columns = prop_sig_corr,
              decimals = 1)

# how often is the test significantly different (after correction) pairs with same vs diff prop of generics
condition_pairs_results %>% 
  group_by(same_prop_generics) %>% 
  summarize(sig_corr_tests = sum(p.value_sig_corr),
            total_tests = n(),
            prop_sig_corr = sig_corr_tests/total_tests) %>% 
  
  # pretty table
  gt() %>% 
  fmt_percent(columns = prop_sig_corr,
              decimals = 1)
```


## Study 6 conditions (replication)

Three of the conditions (baseline, 0/16, 16/16) in this study (*n* = 32-35/condition) are replications of the conditions (baseline, specific, generic conditions) in Study 6 (*n* = 90-99/condition). In Study 6, prevalence was rated higher in the generic condition than the baseline condition than the specific condition, respectively. 

```{r data-study-6}
# filter to baseline, 0/16, 16/16
data_study_6 <- data_tidy %>% 
  filter(condition %in% c("baseline", "0/16", "16/16")) %>% 
  # order condition for plotting
  mutate(condition = condition %>% 
           factor(levels = c("16/16", "baseline", "0/16")))

data_study_6 %>% 
  group_by(condition) %>% 
  summarize(count = n_distinct(participant)) %>% 
  arrange(desc(condition))
```

```{r plot-study-6}
# plot data
data_study_6 %>% 
  
  # make plot
  ggplot(aes(x = prevalence,
             fill = prop_generics)) + 
  facet_wrap(vars(condition)) +
  
  # add density plots
  # geom_density(adjust = 1/2) + 
  geom_histogram(binwidth = .1) + 
  scale_fill_gradient(name = "proportion\n of generics,\n vs specifics\n",
                      low = "#1f77b4", high = "#ff7f0e") +
  
  # remove default facet row/column strip labels...
  theme(
    strip.background = element_blank(),
    strip.text.x = element_blank(),
    strip.text.y = element_blank(),
  ) +
  # ...in favor of in-facet labels
  geom_text(data = data_study_6 %>% distinct(condition, prop_generics),
            aes(label = if_else(
              condition == "baseline", "baseline",
              glue::glue('{condition} generics'))),
            x = .5, y = Inf, vjust = 1.5, size = 3) +
  
  # customize axes
  theme(legend.title = element_text(size = 14),
        legend.text = element_text(size = 12),
        axis.title.x = element_text(size = 10),
        axis.minor.ticks.x.bottom = element_line(size = .5), 
        axis.text.x = element_text(size = 8, hjust = c(0, 1), vjust = .8),
        plot.caption = element_text(size = 8)) +
  scale_y_continuous(expand = c(0, 0, 0.3, 0)) +
  scale_x_continuous(breaks = c(0, 1), minor_breaks = c(.5), expand = c(0,0),
                     labels = label_percent()) +
  guides(
    x = guide_axis(minor.ticks = TRUE),
    alpha = "none"
  ) +
  
  # add title
  ggtitle("Prevalence by condition",
          "Study 6 replication conditions only") +
  labs(caption = "collapsing across 16 test features")
```

After subsetting to the Study 6 conditions, we do replicate the main effect of condition ($\chi$(2) = 12.61, *p* = .0018). The 16/16 condition reported marginally higher prevalence judgments compared to baseline (*z* = 2.19, *p* = .085), and significantly higher compared to 0/16 condition (*z* = 3.51, *p* = .0013). 

Unlike in Study 6, the baseline and 0/16 conditions were not statistically different from each other (*z* = 1.33, *p* = .56). 

```{r analysis-study-6, echo=TRUE, include=TRUE}
# same analysis as study 6
model <- 
  glmmTMB(prevalence ~ condition + (1|participant) + (1|test_feature),
          data = data_study_6, 
          family = beta_family(link = "logit")) 

model %>% 
  Anova()

model %>% 
  emmeans("condition") %>% 
  pairs(adjust = "bonferroni") %>% 
  summary()
```

## Extreme conditions only

Subsetting to the extreme conditions where the proportion of generics was 0% or 100% (0/4, 0/8, 0/12, 0/16, 4/4, 8/8, 12/12, 16/16).

```{r data-extreme-only}
# filter out 0% and 100% generic
data_extreme_only <- data_tidy %>% 
  filter(prop_generics == 0 | prop_generics == 1)

data_extreme_only %>% 
  group_by(condition) %>% 
  summarize(count = n_distinct(participant)) %>% 
  arrange(desc(condition))
```

When each entered on their own as lone predictors, the raw number of generics (*z* = 5.33, *p* < .001), raw number of specifics (*z* = -5.13, *p* < .001), and the proportion of generics to specifics (*z* = 5.71, *p* < .001) were each significant in predicting prevalence judgments. 

When pitted against each other in the same model, the **proportion of generics** to specifics remains a significant predictor of prevalence judgments (*z* = 2.21, *p* = .027), while the **raw number of generics** does not (*z* = 1.00, *p* = .32).

```{r analysis-extreme-only-simple, echo = TRUE, include = TRUE}
# raw number of generics
glmmTMB(prevalence ~ num_generics + (1|participant) + (1|test_feature),
        data = data_extreme_only, 
        family = beta_family(link = "logit")) %>% 
  summary()

# raw number of specifics
glmmTMB(prevalence ~ num_specifics + (1|participant) + (1|test_feature),
        data = data_extreme_only, 
        family = beta_family(link = "logit")) %>% 
  summary()

# proportion of generics
glmmTMB(prevalence ~ prop_generics + (1|participant) + (1|test_feature),
        data = data_extreme_only, 
        family = beta_family(link = "logit")) %>% 
  summary()
```

```{r analysis-extreme-num-vs-prop-generics, echo = TRUE, include = TRUE}
# raw number vs proportion of generics
glmmTMB(prevalence ~ num_generics + prop_generics + (1|participant) + (1|test_feature),
        data = data_extreme_only, 
        family = beta_family(link = "logit")) %>% 
  summary()
```

## Mixed conditions only

Mixed conditions (4/8, 4/12, 4/16, 8/12, 8/16, 12/16) have heightened contrast between generic and specific statements, since participants see both types of statements. 

```{r data-mixed-only}
# filter out 0% and 100% generic
data_mixed_only <- data_tidy %>% 
  filter(prop_generics != 0 & prop_generics != 1)

data_mixed_only %>% 
  group_by(condition) %>% 
  summarize(count = n_distinct(participant)) %>% 
  arrange(desc(condition))
```

After subsetting the sample to just mixed conditions (n = `r length(unique(data_mixed_only$participant))` total), neither raw numbers of generics, raw numbers of specifics, nor the proportion of generics to specifics were statistically significant in predicting prevalence judgments on their own (*p*s > .31). 

```{r analysis-mixed-only-simple, echo = TRUE, include = TRUE}
# raw number of generics
glmmTMB(prevalence ~ num_generics + (1|participant) + (1|test_feature),
        data = data_mixed_only, 
        family = beta_family(link = "logit")) %>% 
  summary()

# raw number of specifics
glmmTMB(prevalence ~ num_specifics + (1|participant) + (1|test_feature),
        data = data_mixed_only,
        family = beta_family(link = "logit")) %>% 
  summary()

# proportion of generics
glmmTMB(prevalence ~ prop_generics + (1|participant) + (1|test_feature),
        data = data_mixed_only,
        family = beta_family(link = "logit")) %>% 
  summary()
```

```{r analysis-mixed-only-num-vs-prop-generics, echo = TRUE, include = TRUE}
# raw number vs proportion of generics
glmmTMB(prevalence ~ num_generics * prop_generics + (1|participant) + (1|test_feature),
        data = data_mixed_only,
        family = beta_family(link = "logit")) %>% 
  summary()
```

```{r analysis-mixed-only-generics-vs-specifics, echo = TRUE, include = TRUE}
# raw number of generics vs raw number of specifics
glmmTMB(prevalence ~ num_generics + num_specifics + (1|participant) + (1|test_feature),
        data = data_mixed_only,
        family = beta_family(link = "logit")) %>%  
  summary()
```

## Training features

Participants saw some subset of 16 training features - anywhere from 0 to 16 of the full list of 16 - with subsets randomly selected. 

Theoretically, the particular training features received might have an effect on prevalence judgments. Of note, the conditions with fewer total training utterances contain significant variability in which training features were seen, while the conditions with more total training utterances have less variability (with all participants in any of the 16 utterance conditions all seeing the same features). 

Random effects to account for:
* different test features may have different prevalences --> random intercepts per test feature
* different participants may rate prevalence differently --> random intercepts per participant
* total number of utterances heard may correlate with variability between participants in prevalence ratings, since conditions with fewer total utterances provided different training features more variability between-participants in the training --> random slopes of __ per total number of utterances
* different training features may increase or decrease the overall prevalence

Are the effects above robust after accounting for additional variance in the training structure?

```{r dummy-coding}
# dummy code whether each training feature was mentioned
data_tidy_dummy <- data_tidy %>%
  # create new column for manipulating
  mutate(training_feature = training_features_order) %>%
  # separate training features into long format
  separate_longer_delim(training_feature, "|") %>%
  
  # mark all these training features as present
  mutate(training_feature_present = TRUE) %>%
  
  # fill in missing training features as not present
  complete(nesting(!!!syms(setdiff(names(.), c("training_feature",
                                               "training_feature_present")))),
           training_feature,
           fill = list(training_feature_present = FALSE)) %>% 
  
  # remove NA as training feature values
  filter(!is.na(training_feature)) %>%
  
  # pivot wide to get dummy columns
  pivot_wider(names_from = training_feature, 
              names_prefix = "trained_",
              values_from = training_feature_present) %>% 
  
  unnest(starts_with("trained_")) 

# get training dummy variables
trained_variables <- data_tidy_dummy %>% 
  select(starts_with("trained_")) %>% 
  colnames()
```

The proportion of generics to specifics was marginal in predicting prevalence judgments (*z* = 1.88, *p* = .061), while the number of generics was not significant (*z* = 0.94, *p* = .35) in a beta regression with random slopes for the total utterances heard, in addition to random intercepts per participant and test feature.

```{r analysis-total-utt}
# num vs prop generic, w random effects for the presence of any particular training feature
glmmTMB(prevalence ~ num_generics + prop_generics + (num_generics|total_utt) + (prop_generics|total_utt) + (1|participant) + (1|test_feature),
        data = data_tidy_dummy,
        family = beta_family(link = "logit")) %>% 
  summary()
```


With 16 random intercepts for whether each of the training features was seen or not, the proportion of generics to specifics is marginal in predicting prevalence judgments (*z* = 1.81, *p* = .0070) and the raw number of generics is not significant (*z* = 1.19, *p* = .23).

```{r analysis-training-features-random}
# num vs prop generic, w random effects for the presence of any particular training feature
formula_str <- paste("prevalence ~ num_generics + prop_generics + ",
                     "(1 + num_generics + prop_generics || participant) + ",
                     "(1 + num_generics + prop_generics || test_feature) + ",
                     paste0("(1|", trained_variables, ")", collapse = " + "))
formula <- as.formula(formula_str)

glmmTMB(formula,
        data = data_tidy_dummy,
        family = beta_family(link = "logit")) %>% 
  summary()
```

Did any particular training features predict prevalence judgments? No (*p*s > .19). 

```{r analysis-training-features-main}
# does presence of any particular training feature matter?
formula_str <- paste("prevalence ~", paste(trained_variables, collapse = " + "), "+ (1|participant) + (1|test_feature)")
formula <- as.formula(formula_str)

glmmTMB(formula,
        data = data_tidy_dummy,
        family = beta_family(link = "logit")) %>% 
  summary()

# get list of test features
data_tidy %>% 
  distinct(test_feature)
```

Additional possible analyses to do: 

* Within a condition, find mean prevalence difference for people who saw feature X vs people who didn't see the feature --> then average that, across conditions

* feature effects are probably bigger for conditions with fewer counts

* could try to put more limitations on which features are seen in conditions w fewer counts - 


## Test features order effects

All participants saw and rated the prevalence of the same set of 16 test features, in random order. Did the order of test feature/prevalence judgment questions matter for prevalence judgments? No. 

```{r analysis-test-order-effects}
glmmTMB(prevalence ~ num_generics * prop_generics * test_feature_order + (1|participant) + (1|test_feature),
        data = data_tidy,
        family = beta_family(link = "logit")) %>% 
  summary()
```


# Power analysis

What is the smallest effect size of interest?

Bootstrapped power analysis to detect the following effects:

* main effect of condition
* main effect of proportionality, in same model as count
* main effect of proportionality, in same model as count - in mixed conditions only

```{r power-analysis, eval = FALSE}
# set parameters
simulations <- 300
sample_size_per_condition <- c(20, 30, 40)

# set up table of parameters
power_setup <- crossing(
  alpha = 0.05, # p-value threshold
  sample_size_per_condition = sample_size_per_condition, # test these sample sizes
  simulation = rep(1:simulations, sample_size_per_condition %>% length()) # n simulations per each of the tested sample sizes
)

# get list of conditions
conditions <- sort(unique(data_tidy$condition))

# create a function to resample specified sample size and run analyses on the resample
bootstrap_analysis <- function(sample_size_per_condition, alpha = 0.05, simulation = NULL) {
  # iterating over conditions, resample participants in that condition to reach specified sample size
  resampled_data <- purrr::map_dfr(conditions, function(cond) {
    # get list of participants in condition
    participants_in_cond <- data_tidy %>%
      filter(condition == cond) %>%
      pull(participant) %>%
      unique()
    # construct list of participants to resample (with replacement)
    resample_participants_list <- sample(participants_in_cond,
                                         sample_size_per_condition,
                                         replace = TRUE)
    # resample those participants & bind into df
    map_dfr(resample_participants_list, function(participant) {
      data_tidy %>%
        filter(participant == participant)
    })
  })

  # run models & pull p-values from each model
  analysis_results <- tibble(
    # condition
    condition = glmmTMB(prevalence ~ condition + (1|participant) + (1|test_feature),
                        data = resampled_data,
                        family = beta_family(link = "logit")) %>%
      Anova() %>%
      pull(`Pr(>Chisq)`),
    
    # prop generics
    prop_generics = summary(glmmTMB(prevalence ~ prop_generics + (1|participant) + (1|test_feature),
                                    data = resampled_data,
                                    family = beta_family(link = "logit")))$coefficients$cond["prop_generics", "Pr(>|z|)"],
    
    # prop generics, controlling for num generics
    prop_generics_ctrl = summary(glmmTMB(prevalence ~ prop_generics + num_generics + (1|participant) + (1|test_feature),
                                         data = resampled_data,
                                         family = beta_family(link = "logit")))$coefficients$cond["prop_generics", "Pr(>|z|)"]
    )

  return(analysis_results)
}


# run the function using the parameters we set up in the power table
power_results <- power_setup %>%
  mutate(analysis_results = pmap(power_setup, bootstrap_analysis)) %>%
  unnest(cols = c(analysis_results))

# for each sample size & analysis, calculate power
power_analysis <- power_results %>%
  group_by(sample_size_per_condition) %>%
  
  # power = percentage of times p < .05
  summarize(condition = sum(condition < .05) / n(),
            prop_generics = sum(prop_generics < .05) / n(),
            prop_generics_ctrl = sum(prop_generics_ctrl < .05) / n())

# export to csv
write_csv(power_analysis, file = "study8_power_analysis.csv")
```





# Footnotes

```{r}
sessionInfo()
```