---
title: "Compgenerics study 6 analysis"
author: "Jessica Stephenson & Marianna Zhang"
output:
  pdf_document:
    toc: true
  word_document:
    toc: true
  html_document:
    toc: true
    toc_float:
      collapsed: false
---

```{r libraries, include=FALSE}
library(here)       # directory management

library(janitor)    # data cleaning
library(scales)     # percent conversion

library(tidyverse)  # data wrangling & visualization

library(car)        # anova type II-III
library(glmmTMB)    # beta mixed effects models
library(lmerTest)   # lmer with p-value
library(emmeans)    # pairwise comparisons
```


```{r setup, include=FALSE}
# don't show code or warnings/messages in knitted doc by default
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE)

knitr::opts_template$set(
  plot = list(
    echo = FALSE,
    results = TRUE),
  analysis = list(
    echo = TRUE,
    results = FALSE)
)


# prevent scientific notation for numerals
options(scipen = 999)

# format p-values for reporting
format_p <- function(p) { 
  if (p < .001) {
    return("< .001")
  } else {
    return(paste0("= ", round(p, digits = 3)))
  }
}
```


# Study 6 methods (Jess)

```{r summary-statistics-6, opts.label='analysis'}
study6 <- read.csv(here("data", "full_study6.csv"))

# report n
n6 <- nrow(study6)
s6_generic <- sum(study6$condition == "generic")
s6_specific <- sum(study6$condition == "specific")
s6_baseline <- sum(study6$condition == "baseline")

#report age breakdown
mean_age6 <- mean(study6$Age, na.rm=TRUE) #need to remove -1
sd_age6 <- sd(study6$Age, na.rm=TRUE) #need to remove -1
min_age6 <- 18 #hard coded, weird response says age is -1
max_age6 <- max(study6$Age, na.rm = TRUE)


#report sex breakdown
n_fem6 <- (sum(study6$Sex=="Female",na.rm=T)/n6)*100
n_male6 <- (sum(study6$Sex=="Male", na.rm=T)/n6)*100
 
#report ethnicity breakdown
race6 <- xtabs(~Ethnicity.simplified, study6)
prop.table(race6)
  
#report gender breakdown
sex6 <- xtabs(~Sex, study6)
prop.table(sex6*100)

```

-   Study 6 is a replication of study 5 with an additional "baseline" condition added. In this condition, participants were not shown any video, and immediately completed the induction task.
-   Adult participants (n = `r n6`; `r round(n_fem6, digits = 1)`%
    female, `r round (n_male6, digits = 1)`% male; M~age~ =
    `r round(mean_age6, digits = 2)`, SD~age~ =
    `r round(sd_age6, digits = 2)`, range = `r min_age6`-`r max_age6`)
    split into three conditions: generic (n = `r s6_generic`), specific
    (n = `r s6_specific`), or baseline (n = `r s6_baseline`)


# Study 6 analysis (Jess)
```{r, opts.label='analysis'}
##induction task
s6_ind_long <- read.csv(here("data", "ind_ordered_s6.csv")) 
s6_ind_long$trial <- as.factor(s6_ind_long$trial)

#set levels
levels(s6_ind_long$trial) <- list(trial.1 = "1", trial.2 = "2", trial.3 = "3", trial.4 = "4", trial.5 = "5", trial.6 = "6", trial.7 = "7", trial.8 = "8", trial.9 = "9", trial.10 = "10", trial.11 = "11", trial.12 = "12", trial.13 = "13", trial.14 = "14", trial.15 = "15", trial.16 = "16", trial.17 = "17")

s6_ind_long <- s6_ind_long %>% 
  mutate(condition = factor(condition,
                            levels = c("generic", "specific", "baseline")))

#summary stats
s6_ind_long %>%
  dplyr::group_by(condition) %>%
  dplyr::summarize(mean=mean(prevalence, na.rm = TRUE))

#multilevel linear model with a random intercept for ID
model<-lmer(prevalence ~ condition + (1|ID), data=s6_ind_long)
summary(model)
Anova(model)
```

```{r violin-plot, opts.label="plot"}
#plot of means
ggbetweenstats(
  data = s6_ind_long,
  x = condition,
  y = prevalence,
  type = "parametric",
  var.equal = TRUE,
  plot.type = "boxviolin",
  pairwise.comparisons = TRUE,
  pairwise.display = "significant",
  centrality.plotting = TRUE,
  bf.message = FALSE,
  title = "Aggregate Induction Results Study 6"
)

#visualizing trial order effect
s6_ind_long %>% 
ggplot(aes(x = trial, y = prevalence, fill = condition)) + 
  geom_boxplot() +
   theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1,))+
  ggtitle("Study 6: Prevalence by Trial") +
  facet_wrap(~condition)



#basic violin plot
ggplot(s6_ind_long, aes(prevalence, condition,fill=condition, color = condition),show.legend = FALSE) + 
  geom_violin(alpha=.9, show.legend = FALSE)+
  scale_y_discrete(labels=c("one_obs" = "one observation"))+
  stat_summary(fun.data = "mean_cl_boot", fun.args=list(B=1000), geom = "errorbar",width = .5, colour = "black", show.legend = FALSE) + #bootstrapped CI
  stat_summary(fun = "mean", geom = "point", colour = "black", size = 0.2, show.legend = FALSE) + #mean
  labs(x = "Prevalence Rating", y = "Condition")+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) + ggtitle("Aggregate Induction Results Study 6")

```



# Study 6 analysis (Marianna)

```{r import-model-means}
# import model simulated means
df_prag_feature <- read_csv(here("model/scratch/study 6", "df_prag_feature.csv"))
df_lit_feature <- read_csv(here("model/scratch/study 6", "df_lit_feature.csv"))
df_base_feature <- read_csv(here("model/scratch/study 6", "df_base_feature.csv"))

# get model means per condition, feature
df_prag_feature_means <- df_prag_feature %>% 
  group_by(condition, feature) %>% 
  summarize(prag_prevalence_mean = mean(prevalence, na.rm = TRUE))

df_lit_feature_means <- df_lit_feature %>%
  group_by(condition, feature) %>% 
  summarize(lit_prevalence_mean = mean(prevalence, na.rm = TRUE))

df_base_feature_means <- df_base_feature %>%
  group_by(condition, feature) %>% 
  summarize(base_prevalence_mean = mean(prevalence, na.rm = TRUE))
```

```{r clean-data}
# clean data
s6_data_tidy <- study6 %>% 
  
  # reformat to tibble
  as.tibble() %>% 
  clean_names() %>% 
  rename(participant = id) %>% 
  
  # tidy
  pivot_longer(cols = live_caves:paint_hands,
               names_to = "feature",
               values_to = "prevalence") %>% 
  relocate(feature:prevalence,
          .after = "condition") %>% 
  
  # rescale, truncate prevalence
  mutate(prevalence = prevalence / 100) %>% 
  mutate(prevalence = case_when(prevalence == 0 ~ 0.01,
                                prevalence == 1 ~ 0.99,
                                TRUE ~ prevalence)) %>% 
  
  # join in model condition/feature means
  left_join(df_prag_feature_means, by = c("condition", "feature")) %>%
  left_join(df_lit_feature_means, by = c("condition", "feature")) %>%
  left_join(df_base_feature_means, by = c("condition", "feature")) %>% 
  
  relocate(contains("prevalence"),
           .after = "feature")

# get data means per condition, feature
s6_data_per_condition_feature <- s6_data_tidy %>% 
  group_by(condition, feature) %>% 
  summarize(prevalence_mean = mean(prevalence, na.rm = TRUE)) %>% 
  
  # join in model means
  left_join(df_prag_feature_means, by = c("condition", "feature")) %>%
  left_join(df_lit_feature_means, by = c("condition", "feature")) %>%
  left_join(df_base_feature_means, by = c("condition", "feature"))
```


## Behavioral analyses

```{r lmer, eval=FALSE, opts.label="analysis"}
# analyses presented in CogSci paper

# linear mixed-effects model
lmer_condition <-
  lmer(prevalence ~ condition + (1|participant) + (1|feature),
       data=s6_data_tidy)

# main effect of condition?
lmer_condition %>%
  Anova()

# pairwise comparisons, corrected since exploratory
lmer_condition %>%
  emmeans("condition") %>%
  pairs(adjust = "bonferroni") %>%
  summary()
```


```{r glm, opts.label="analysis"}
# beta mixed-effects model
glm_condition <-
  glmmTMB(prevalence ~ condition + (1|participant) + (1|feature), 
        data = s6_data_tidy, 
        family = beta_family(link = "logit")) 

# main effect of condition?
glm_condition %>% 
  Anova()

# pairwise comparisons, corrected since exploratory
glm_condition %>% 
  emmeans("condition") %>% 
  pairs(adjust = "FDR") %>% 
  summary()
```


## Model comparison

```{r model-means-vs-data}
# base model vs data
glm_base <- 
  glmmTMB(prevalence ~ base_prevalence_mean + (1|participant), 
          data = s6_data_tidy, 
          family = beta_family(link = "logit"))

# literal listener vs data
glm_lit <- 
  glmmTMB(prevalence ~ lit_prevalence_mean + (1|participant), 
          data = s6_data_tidy, 
          family = beta_family(link = "logit"))

# pragmatic listener vs data
glm_prag <- 
  glmmTMB(prevalence ~ prag_prevalence_mean + (1|participant), 
          data = s6_data_tidy, 
          family = beta_family(link = "logit"))

# model comparison: base vs lit
# anova(glm_base, glm_lit)

tibble(
  model = c("base", "lit", "prag"),
  log_lik = c(logLik(glm_base), logLik(glm_lit), logLik(glm_prag)),
  AIC   = c(AIC(glm_base), AIC(glm_lit), AIC(glm_prag)),
  BIC   = c(BIC(glm_base), BIC(glm_lit), BIC(glm_prag))
)
```









# Power analyses off of Study 6 (Marianna)

Bootstrapped power analyses off of study 6

## Study 6 (preregistered) power analysis

We can plan sample size for a pre-registered version of Study 6 by bootstrapping off of the existing Study 6 data to simulate what sample size is needed to achieve 90% power on the following effects:

* main effect of condition in prevalence (in mixed effects beta regression with random intercepts per participant and per test feature)

* follow-up comparison: generic vs baseline difference in prevalence

* follow-up comparison: specific vs baseline difference in prevalence

```{r eval=FALSE}
# set the parameters
conditions <- c("generic", "baseline", "specific")
sample_size_per_cond <- c(100, 125, 150)
simulations <- 300 # per sample size

power <- crossing(
  alpha = 0.05,
  sample_size_per_cond = sample_size_per_cond, # test these sample sizes
  simulation = rep(1:simulations, length(sample_size_per_cond)) # __ simulations per each sample size
)

# create a function to sample individual participants from pilot data and run analyses on the resample
bootstrap_analysis <- function(sample_size_per_cond, alpha = 0.05, simulation = NULL){
  
  # for each condition conditions, resample participants in that condition to reach specified sample size
  resampled_data <- purrr::map_dfr(conditions, function(cond) {
    
    # get list of original participants in condition
    participants_in_cond <- s6_data_tidy %>%
      filter(condition == cond) %>%
      distinct(participant) %>% 
      pull(participant)
    
    # construct list of participants to resample (with replacement, so might contain duplicates)
    resample_participants_in_cond <- 
      tibble(
        observation_in_cond = c(1:sample_size_per_cond),
        participant = sample(participants_in_cond,
                             sample_size_per_cond,
                             replace = TRUE)
      ) 
    
    # return data for those participants
    resample_participants_in_cond %>% 
      left_join(s6_data_tidy, by = "participant")
    
  })
  
  # resampled_data <- resampled_data %>% 
  #   # messy way to label each individual observation, even if resampled from same participant: use interaction of observation in condition and participant ID to assign a unique label to each observation across the whole dataset
  #   mutate(observation = dplyr::dense_rank(interaction(observation_in_cond, participant))) 
  
  
  
  # run behavioral analyses
  glmm_condition <- 
    glmmTMB(prevalence ~ condition + (1|participant) + (1|feature),
            data = resampled_data,
            family = beta_family(link = "logit"))
  
  glmm_condition_aov <- glmm_condition %>% 
    Anova()
  
  glmm_condition_pairs <- glmm_condition %>% 
    emmeans("condition") %>% 
    pairs(adjust = "none") %>% # no adj since prereg
    summary()
  
  
  
  # # compare models vs data
  # 
  # # base model vs data
  # glm_base <- 
  #   glmmTMB(prevalence ~ base_prevalence_mean + (1|participant), 
  #           data = resampled_data, 
  #           family = beta_family(link = "logit"))
  # 
  # # literal listener vs data
  # glm_lit <- 
  #   glmmTMB(prevalence ~ lit_prevalence_mean + (1|participant), 
  #           data = resampled_data, 
  #           family = beta_family(link = "logit"))
  # 
  # # pragmatic listener vs data
  # glm_prag <- 
  #   glmmTMB(prevalence ~ prag_prevalence_mean + (1|participant), 
  #           data = resampled_data, 
  #           family = beta_family(link = "logit"))
  # 
  # 
  # # run model comparisons
  # model_comp <- tibble(
  #   model = c("base", "lit", "prag"),
  #   AIC   = c(AIC(glm_base), AIC(glm_lit), AIC(glm_prag)),
  #   BIC   = c(BIC(glm_base), BIC(glm_lit), BIC(glm_prag))
  # )
  
  
  
  # pull critical values to evaluate from each analysis
  results <- tibble(
    # main effect of condition
    condition = glmm_condition_aov %>% 
      pull(`Pr(>Chisq)`),
    
    # baseline vs generic
    baseline_vs_generic = glmm_condition_pairs %>% 
      filter(contrast == "baseline - generic") %>% 
      pull(p.value),
    
    # baseline vs specific
    baseline_vs_specific = glmm_condition_pairs %>% 
      filter(contrast == "baseline - specific") %>% 
      pull(p.value),
    
    
    # # base vs lit AIC, who's lower
    # base_vs_lit_aic = if_else(
    #   model_comp %>% filter(model == "base") %>% pull(AIC) >
    #     model_comp %>% filter(model == "lit") %>% pull(AIC),
    #   "lit",
    #   "base"),
    # 
    # # base vs lit BIC, who's lower
    # base_vs_lit_bic = if_else(
    #   model_comp %>% filter(model == "base") %>% pull(BIC) >
    #     model_comp %>% filter(model == "lit") %>% pull(BIC),
    #   "lit",
    #   "base"),
    # 
    # # lit vs prag AIC, who's lower
    # lit_vs_prag_aic = if_else(
    #   model_comp %>% filter(model == "lit") %>% pull(AIC) >
    #     model_comp %>% filter(model == "prag") %>% pull(AIC),
    #   "prag",
    #   "lit"),
    # 
    # # lit vs prag BIC, who's lower
    # lit_vs_prag_bic = if_else(
    #   model_comp %>% filter(model == "lit") %>% pull(BIC) >
    #     model_comp %>% filter(model == "prag") %>% pull(BIC),
    #   "prag",
    #   "lit")
    
    
    )
  
  return(results)
}

power_exp <- power %>% 
  mutate(results = pmap(power, bootstrap_analysis)) %>% # run the function using the parameters we set up in the power table
  unnest(cols = c(results))

power_results <- power_exp %>% 
  group_by(sample_size_per_cond) %>%
  summarize(condition = sum(condition < .05) / n(),
            baseline_vs_generic = sum(baseline_vs_generic < .05) / n(),
            baseline_vs_specific = sum(baseline_vs_specific < .05) / n())
            
            # base_vs_lit_aic = sum(base_vs_lit_aic == "lit") / n(),
            # base_vs_lit_bic = sum(base_vs_lit_bic == "lit") / n(),
            # lit_vs_prag_aic = sum(lit_vs_prag_aic == "prag") / n(),
            # lit_vs_prag_bic = sum(lit_vs_prag_bic == "prag") / n())

write.csv(power_results, file = "study6_power_results.csv")

power_results
```

## Study 8 power analysis

```{r eval=FALSE}
# set the parameters
alpha <- 0.05
simulations <- 300

power <- crossing(
  alpha = alpha,
  sample_size = c(20, 25, 30, 40, 50), # test these sample sizes
  simulation = rep(1:simulations, 5) # 1000 simulations per each of 5 tested sample sizes
)

# create a function to sample individual participants from pilot data and run analyses on the resample
bootstrap_analysis <- function(sample_size, alpha = 0.05, simulation = NULL){
  # resample sample_size number of participants from pilot data, with replacement
  resample <- bind_rows(s6_ind_long %>% 
                          filter(condition == "generic") %>% 
                          slice_sample(n = sample_size, replace = TRUE),
                        s6_ind_long %>% 
                          filter(condition == "specific") %>% 
                          slice_sample(n = sample_size, replace = TRUE)) %>% 
    mutate(observation = row_number())
  
  # run analyses on each measure, pull p-values from each analysis
  results <- tibble(
    prevalence_main_effect = lmer(prevalence ~ condition + (1|question), 
                                  data = resample) %>% 
      Anova() %>%
      pull(`Pr(>Chisq)`)
    )
  
  return(results)
}

power_exp <- power %>% 
  mutate(results = pmap(power, bootstrap_analysis)) %>% # run the function using the parameters we set up in the power table
  unnest(cols = c(results))

power_results <- power_exp %>% 
  group_by(sample_size, contrast) %>%
  summarize(prevalence_main_effect = sum(prevalence_main_effect < .05) / n())

write.csv(power_results, file = "study8_power_results.csv")
```
